### 2025-01-10 README.Rmd
update 2025-01-10 09:52:05.955697

```{r, echo = FALSE}
knitr::include_graphics("https://github.com/cjvanlissa/worcs/raw/master/paper/workflow_graph/workflow.png")
```

>>>>

```{r, echo = FALSE, fig.alt="A diagram of the WORCS workflow."}
knitr::include_graphics("https://github.com/cjvanlissa/worcs/raw/master/paper/workflow_graph/workflow.png")
```
